Discrimination in police award nomination in Chicago

### 2024-02-14 outputs/paper/paper.qmd
Changed table style (need to choose one table stlye for Table 1), Added tables for lm models

library(tidyverse)
library(haven)
library(usethis)
library(here)
library(knitr)
library(truncnorm)
```

@@

kable(baseline_characteristics)
```

@@

```{r}
#| echo: false
modified_model <- lm(awd_perf ~ Black + Female + Hisp + Asian, data = all_officer_year)
modified_model
```
```{r}
#| echo: false
black_female <- lm(awd_perf ~ Black + Female + Black:Female, 
                   data = all_officer_year)
black_female
```
From this, we form a regression model to estimate the disparity gaps in award nomination between majority (white and/or male) and minority (black and/or female). The following model is the regression: y = beta0 + beta1*black + beta2*female + beta3*Hispanic + beta4*Asian where y is the number of award nomination received by an officer in one year.

>>>>

library(tidyverse)
library(haven)
library(usethis)
library(here)
library(knitr)
library(truncnorm)
library(flextable)
```

@@

kable(baseline_characteristics)
as_flextable(baseline_characteristics)
```

@@

```{r}
#| echo: false
modified_model <- lm(awd_perf ~ Black + Female + Hisp + Asian, data = all_officer_year)
as_flextable(modified_model)
```
```{r}
#| echo: false
black_female <- lm(awd_perf ~ Black + Female + Black:Female, 
                   data = all_officer_year)
as_flextable(black_female)
```
From this, we form a regression model to estimate the disparity gaps in award nomination between majority (white and/or male) and minority (black and/or female). The following model is the regression: y = beta0 + beta1*black + beta2*female + beta3*Hispanic + beta4*Asian where y is the number of award nomination received by an officer in one year.
